InnoDB's Full Text Search overview (with Shiny/R)

### 2016-04-19 article.rmd
Added files and compatibility with ansible

---
title: "InnoDB's Full Text Search Dynamic article with Shiny/R"
author: "Emanuel Calvo - Pythian"
date: "January 3rd, 2016"
output: html_document
runtime: shiny
---

@@

 **BETA - NOT FINAL**

@@

Thanks db4free.net for the MySQL free online database!

>>>>

---
title: "InnoDB's Full Text Search overview (with Shiny/R)"
author: "Emanuel Calvo - Pythian"
date: "January 3rd, 2016"
output: html_document
runtime: shiny
---

@@

@@
